OSF management

### 2021-02-25 docs/methods_norm_prod/methods_norm_prod.Rmd
:bento: - upload methods description to the OSF

---
title: "Production study: Methodological details"
author: ""
date: "9/17/2020"
output:
  bookdown::pdf_document2:
    number_sections: true
    keep_tex: true
header-includes:
  - \usepackage{expex}
  - \lingset{everygla=,everyglpreamble=\it}
  - \usepackage[export]{adjustbox}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.pos = "tbp")
options(tinytex.verbose = TRUE)
```

@@

This document describes the methodological details of the production study, which generated the data your team will analyze for the *Many Speech Analyses* project.

<!-- TODO: link to OSF wiki for overview of the norming and production studies -->
Although the details of the norming study (run prior to the production study, see OSF Wiki) might not be directly relevant for your analysis, we provide an outline of the norming study methods in Appendix \@ref(norming) for context.

# Research question

This study investigated whether speakers modify speech to signal atypical referents.
Concretely, we asked whether the acoustic profile of an utterance with an atypical referent like *blue banana* is different from one with a typical referent such as *yellow banana*.

# Participants

# Procedure

In this production study, participants interacted with the experimenter in German.
Participants were seated in front of a computer screen.
The experimenter sat at the opposite side of the table in front of another computer screen.
The participants and the experimenter could not see each other nor each others' screens.
The participants had to verbally instruct the experimenter to select a specified target object out of four visually presented objects.
The non-target objects differed from the target with respect to their color, their identity, or both.
Objects were referred to using noun phrases that consist of a modifier denoting color and a modified object (e.g. *Gelbe Zitrone* 'yellow lemon', *Rote Gurke* 'red cucumber', *Rote Socken* 'red socks').
These color-object combinations differed with respect to their typicality.
The color-object combinations were either typical (e.g. *Orangene Mandarine* 'orange mandarin'), medium typical (e.g. *Grüne Tomate* 'green tomato'), or atypical (e.g. *Gelbe Kirsche* 'yellow cherry').
The typicality rating of each color-object combination was established, prior to the production experiment, with a norming study (see Appendix \@ref(norming) for details).
Figure \@ref(fig:image0) illustrates combination typicality for a banana, a tomato, and an apricot.

```{r image0, echo = FALSE, fig.align="center", out.width = "60%", fig.cap = "Three examples for typical, medium typical and atypical combinations of colour and object."}

knitr::include_graphics("typicality_examples.png")

```

```{r image1, echo = FALSE, fig.align="center", out.width = "60%", fig.cap = "Test trial: Example screen of a trigger instruction. The trigger instruction is displayed in the middle below the cube. Here, the participants have to instruct the experimenter to move the cube on top of the green sunglasses (indicated by an arrow).", out.extra="frame"}

knitr::include_graphics("sample_experiment_screen_competitor.png")

```

```{r image2, echo = FALSE, fig.align="center", out.width = "60%", fig.cap = "Test trial: Example screen of the test instruction. The target sentence is displayed in the middle of the screen. Now, participants have to instruct the experimenter to move the cube on top of the green avocado (indicated by an arrow).", out.extra="frame"}

knitr::include_graphics("sample_experiment_screen_target.png")

```

# Norming study {#norming}

Here we specify in detail the selection of the stimuli for the production study.

@@

The selection of stimuli was informed by a norming study for which we have chosen twenty fruits or vegetables (henceforth: FOODs) and four other referents (henceforth: NON-FOODs).
Selection criteria were mainly informed by visual discriminability and phonemic composition, such that nouns denoting our objects were supposed to contain as few voiceless segments as possible.

@@

>>>>

---
title: "Methodological details of the norming and production studies"
author: ""
date: "9/17/2020"
output:
  bookdown::pdf_document2:
    number_sections: true
    keep_tex: true
fontsize: 12pt
header-includes:
  - \renewcommand{\familydefault}{\sfdefault}
  - \usepackage{expex}
  - \lingset{everygla=,everyglpreamble=\it}
  - \usepackage[export]{adjustbox}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.pos = "tbp")
knitr::opts_knit$set(root.dir = here::here())
library(here)
options(tinytex.verbose = TRUE)
```

@@

This document describes the methodological details of the norming study and the production study that generated the data your team will analyze for the *Many Speech Analyses* project.

The norming study was run to obtain ratings on the typicality of color/object combinations used to create the experimental categories manipulated in the production study.
The production study then investigated whether speakers modify speech to signal the (a)typicality of the color/object combinations.
Concretely, we asked whether the acoustic profile of an utterance with an atypical referent like *blue banana* is different from one with a typical referent such as *yellow banana*.

<!-- TODO: link to OSF wiki for overview of the norming and production studies -->

# Norming study

Here we specify in detail the selection of the stimuli used in the production study.

@@

The selection of stimuli was informed by a norming study for which twenty fruits or vegetables (henceforth: FOODs) and four other referents (henceforth: NON-FOODs) were chosen.
Selection criteria were mainly informed by visual discriminability and phonemic composition, such that nouns denoting objects were supposed to contain as few voiceless segments as possible.

@@

# Production study

## Participants

## Procedure

In this production study, participants interacted with the experimenter in German.
Participants were seated in front of a computer screen.
The experimenter sat at the opposite side of the table in front of another computer screen.
The participants and the experimenter could not see each other nor each others' screens.
The participants had to verbally instruct the experimenter to select a specified target object out of four visually presented objects.
The non-target objects differed from the target with respect to their color, their identity, or both.
Objects were referred to using noun phrases that consist of a modifier denoting color and a modified object (e.g. *Gelbe Zitrone* 'yellow lemon', *Rote Gurke* 'red cucumber', *Rote Socken* 'red socks').
These color-object combinations differed with respect to their typicality.
The color-object combinations were either typical (e.g. *Orangene Mandarine* 'orange mandarin'), medium typical (e.g. *Grüne Tomate* 'green tomato'), or atypical (e.g. *Gelbe Kirsche* 'yellow cherry').
Figure \@ref(fig:image0) illustrates combination typicality for a banana, a tomato, and an apricot.

```{r image0, echo = FALSE, fig.align="center", out.width = "60%", fig.cap = "Three examples for typical, medium typical and atypical combinations of colour and object."}
knitr::include_graphics(here("figs", "typicality_examples.png"))
```

```{r image1, echo = FALSE, fig.align="center", out.width = "60%", fig.cap = "Test trial: Example screen of a trigger instruction. The trigger instruction is displayed in the middle below the cube. Here, the participants have to instruct the experimenter to move the cube on top of the green sunglasses (indicated by an arrow).", out.extra="frame"}
knitr::include_graphics(here("figs", "sample_experiment_screen_competitor.png"))
```

```{r image2, echo = FALSE, fig.align="center", out.width = "60%", fig.cap = "Test trial: Example screen of the test instruction. The target sentence is displayed in the middle of the screen. Now, participants have to instruct the experimenter to move the cube on top of the green avocado (indicated by an arrow).", out.extra="frame"}
knitr::include_graphics(here("figs", "sample_experiment_screen_target.png"))
```

### 2021-02-25 osf/manage-osf.Rmd
:bento: - upload methods description to the OSF

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
library(osfr)
library(speakr)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
library(here)
library(tidyverse)
library(osfr)
library(speakr)
```

@@

# PDF of norming and production methods

```{r pdf-methods}
file.copy("./docs/methods_norm_prod/methods_norm_prod.pdf", "./osf/data/", overwrite = T)

osf_upload(data_comp, path = "./osf/data/methods_norm_prod.pdf", conflicts = "overwrite", verbose = T)
```
